\Title

### 2016-03-21 manuscript/manuscript.tex
Corrections to last paragraph of conclusion by Val

We applied the method proposed here to estimate the Moho depth for South
America.
Our Moho depth model is in accordance with previous results by
\citet{vandermeijde2013}.
The model fits well the gravity and seismic data in all oceanic regions, the
central portion of the Andean foreland, Patagonia, and coastal and central
parts of Brazil.
However, the model is unable to fit the gravity and seismic data in places with
sharp variations in Moho depth, particularly below the Andes.
This might indicate the improper use of smoothness regularization, as suggested
by the CRUST1.0 synthetic data test, or the presence of crustal or mantle
density anomalies that were unaccounted for during the data corrections.
In the coastal region of Venezuela, along the central Amazon and Solimões
Basins, and in the Paraná Basin, the model is able to fit the gravity data but
differs significantly from the seismic data.
\citet{mariani2013} and \citet{nunn1988} explain these discrepancies in the
Paraná and Amazon Basins, respectively, as high density rocks in the lower
crust.
In general, differences between a gravity and a seismically derived Moho model
may indicate the presence of crustal or mantle density anomalies that were
unaccounted for in the data processing.
Such locations warrant further detailed investigation.

>>>>

We applied the method proposed here to estimate the Moho depth for South
America.
Our estimated Moho depth model is in accordance with previous results by
\citet{vandermeijde2013}.
The model fits well the gravity and seismic data in all oceanic regions, the
central portion of the Andean foreland, Patagonia, and coastal and central
parts of Brazil.
However, the model is unable to fit the gravity and seismic data in places with
sharp variations in Moho depth, particularly below the Andes and in the
boundaries of the main geotectonic provinces of the South American Plate, like
the Borborema province, the Parnaiba Basin, and the São Francisco Craton.
This might indicate that smoothness regularization should not be applied
indiscriminately to the whole model, as suggested by the CRUST1.0 synthetic
data test.
Another reason for the observed misfit might be the presence of crustal or
mantle density anomalies whose gravitational effects were not removed during
the data corrections.
In the coastal region of Venezuela, along the central Amazon and Solimões
Basins, and in the Paraná Basin, our Moho depth model is able to fit the
gravity data but differs significantly from the seismic data.
\citet{mariani2013} and \citet{nunn1988} explain these discrepancies in the
Paraná and Amazon Basins, respectively, as high density rocks in the lower
crust.
In general, differences between a gravity and a seismically derived Moho model
may indicate the presence of crustal or mantle density anomalies that were
unaccounted for in the data processing.
Such locations warrant further detailed investigation.
